---
title: "EcoMetrics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EcoMetrics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This provides a guideline on how to use the package in teaching Regression Modeling and Basic Econometrics Modules for undergraduate students.


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EcoMetrics)
```

# Basic Regression Analysis Concepts

## Fitting Simple Linear Model

A simple linear model given by $Y = \beta_{0} + \beta_{1}X + \varepsilon$ can be fit using the function described below to get the estimates of $\hat{\beta_{0}}$ and $\hat{\beta_{1}}$.


```{r}
simple_model <- ols_model(data = eduperform, "pi", c("hs"))
simple_model
```


## Fitting Multiple Linear Model

Given a Multiple linear regression equation:

$$Y = \beta_{0}+\beta_{1}X_{1} + \beta_{2}X_{2}+...+\beta_{p}X_{p} + \varepsilon$$ one can get the estimate of $\hat{beta}$ given as:

$$\hat{\beta} = (X^{\prime}X)^{-1}X^{\prime}Y$$
```{r}
multiple_model <- ols_model(data = eduperform, "pi", c("hs","ps"))
multiple_model
```


## Model Summary Statistics

The important metrics of a fitted model care given by:

```{r}
ols_model_stats(data = eduperform, "pi", c("hs", "ps"))
```



## Model Summary Statistics

The Model Summary Statistics of the model are given by:

```{r}
ols_model_stats(data = eduperform, "pi", c("hs", "ps"))
```


## F-Statistic Summary

The F-Statistic attributes of the fitted model:

```{r}
ols_model_sig(data = eduperform, "pi", c("hs", "ps"))
```


## Checking Overall Model Significance

```{r}
check_model_sig(data = eduperform, "pi", c("hs", "ps"))
```


## Confidence Intervals of Parameters

```{r}
get_confint(data = eduperform, "pi", c("hs", "ps"))
```


## Obtain Only Significant Parameters

```{r}
get_significant_predictors(data = eduperform, "pi", c("hs", "ps"))
```


## Getting Variance of Coefficients

```{r}
get_coefficients_variance(data = eduperform, "pi", c("hs", "ps"))
```


## Predicting New Observations

```{r}
model <- lm(pi ~ hs + ps, data = eduperform)
newdata <- data.frame(hs =c(2,3,4),ps = c(23,24,12))
predict_dep_var(model, new_data = newdata, level = 0.95)
```



## Model Assumptions

After fitting a multiple linear model it is prudent to check the model assumptions. Here we describe how to do this:


### Normality Assumption

The null hypothesis is that the residuals are normally distributed.

```{r}
model <- lm(pi ~ hs + ps, data = eduperform)
normality_assumption(model)
```


### Heteroscedasticity Assumption

The null hypothesis is that the variance of the residuals is constant (Homoscedastic)

```{r}
model <- lm(pi ~ hs + ps, data = eduperform)
heteroscedasticity_assumption(model)
```


### Multicollonearity Assumption

```{r}
model <- lm(pi ~ hs + ps, data = eduperform)
multicollinearity_assumption(model)
```


### Autocorrelation Assumption

```{r}
model <- lm(pi ~ hs + ps, data = eduperform)
autocorrelation_assumption(model)
```

## Choosing Optimal Linear Regression Model

Often one is supposed to select the optimal model and the criteria is either AIC, BIC or Adjusted R-Squared

```{r}
data(eduperform)
model1 <- lm(pi ~ hs, data = eduperform)
model2 <- lm(pi ~ hs + ps, data = eduperform)
model3 <- lm(pi ~ hs + ps + sh, data = eduperform)
models <- list(model1, model2, model3)
select_optimal_model(models, criterion= "AIC")
```



# Basic Time Series Concepts

This section describes the very basic time series concepts of testing stationarity, plotting ACF and PACF of time series data, fitting ARIMA models and selecting the optimal ARIMA(p,d,q) model.


## Testing Stationarity

We implement the ADF test.

```{r}
data(keconomy)
attach(keconomy)
check_stationarity(UR)
```


## Plotting ACF and PACF of time series data

```{r}
data(keconomy)
attach(keconomy)
ACF_PLOT(UR)
```



```{r}
data(keconomy)
attach(keconomy)
PACF_PLOT(UR)
```



## Fitting ARIMA models

```{r}
data(keconomy)
attach(keconomy)
fit_arima(UR, p=2,d=0,q=3)
```


## Selecting Optimal ARIMA model

```{r}
data(keconomy)
attach(keconomy)
best_arima(UR, max_p = 5, max_d = 2, max_q = 5)
```

